### 2019-09-24 papers/journal/model.tex
First Update for revision
Update on connectedness property

% \textbf{Fusion condition in QBF and synthesis:}
%
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
$\nodef(k,\nlabel(n))$ is true.
%
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
$\edgef(k,M')$ is true.
%
We say $G$ is {\em fuse compatible} if molecules $M$ is divided into
two partitions $Q$ and $R$ such that
for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $.
%
In other words,
molecules are of two types $Q$ and $R$,
%
pairing relations have sets of four molecules such that three
are of type $Q$ and one of type $R$ or vice versa.
%
% This distinction of molecules is due to section~\ref{mol-types}.
%
We call $G$ {\em well-structured} if it is pair compatible, and
for each $(n,M',n') \in \edges$, $n \neq n'$ and
$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
%
In addition to fuse compatibility, the well-structured property requires that
here are no self-loops, and 
each edge carry only those molecules that are present in its source
and destination nodes.
%
An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with its destination node $n'$
and can not fuse with any other node.
%
$\pairs$ models biological possible quadruple of molecules that participate in fusion.
%
Each edge must be uniquely supported by such a quadruple of molecules.
%
We also require three of them to be on the node or edge, and the forth one
to be on the other side of the fusion.
% $\pairs(M'')$ are not active in any other node.

@@

%
We call $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ is reachable from $n$ in $G$.
%
We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and
$|\edges'| < k$, VTS
$(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
%
We will check if a VTS $G$ is $k$-connected or not.
%
The property of $k$-connectedness is a robustness property that one
expects from a biological systems.
%
The property says even after failure of a few edges the system will continue to work.

>>>>

% \textbf{Fusion condition in QBF and synthesis:}
%
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
$\nodef(k,\nlabel(n))$ is true.
%
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
$\edgef(k,M')$ is true.
%
We say $G$ is {\em fuse compatible} if molecules $M$ is divided into
two partitions $Q$ and $R$ such that
for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $.
%
In other words,
molecules are of two types $Q$ and $R$,
%
pairing relations have sets of four molecules such that three
are of type $Q$ and one of type $R$ or vice versa.
%
% This distinction of molecules is due to section~\ref{mol-types}.
%
We call $G$ {\em well-structured} if it is pair compatible, and
for each $(n,M',n') \in \edges$, $n \neq n'$ and
$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
%
In addition to fuse compatibility, the well-structured property requires that
here are no self-loops, and 
each edge carry only those molecules that are present in its source
and destination nodes.
%
An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with its destination node $n'$
and can not fuse with any other node.
%
$\pairs$ models biological possible quadruple of molecules that participate in fusion.
%
Each edge must be uniquely supported by such a quadruple of molecules.
%
We also require three of them to be on the node or edge, and the forth one
to be on the other side of the fusion.

% $\pairs(M'')$ are not active in any other node.

@@

%
We call $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ is reachable from $n$ in $G$.
%
We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and
$|\edges'| < k$, VTS
$(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
%
We use \textit{$e$ edge removal} for removing exactly $e$ present edges from the underlying graph.
%
We will check if a VTS $G$ is $k$-connected or not.
%
The property of $k$-connectedness is a robustness property that one
expects from biological systems.
%
The property says even after failure of a few edges the system will continue to work.
